Self Regulation Ontology Retest Analyses

### 2018-07-25 code/SRO_Retest_Analyses.Rmd
updating stats

```{r}
summary(lm(value~key*similarity,tmp))
effect.size(lm(value~key*similarity,tmp))
```

@@

```{r echo=FALSE}
rm(tmp, comb, t1_2_difference, duplicate_items, duplicate_items_data_t1, duplicate_items_data_t2, extract_items, get_delay_effect)
```

>>>>

```{r}
summary(lm(value~key*similarity,tmp))
```

@@

```{r echo=FALSE}
rm(tmp, comb, t1_2_difference, duplicate_items, duplicate_items_data_t1, duplicate_items_data_t2, extract_items)
```
